---
title: "Word Analysis"
author: "Daniel Chen"
output: 
  html_document: 
    toc: yes
---

```{r, message=FALSE}
library(dplyr)
library(wordcloud)
library(ggplot2)

knitr::opts_chunk$set(fig.width = 8)

rm(list = ls())
if (interactive()) {
  data_loc <- 'output/data.RData'
} else {
  data_loc <- '../output/data.RData'
}

load(data_loc)

```
# Subjects
Subjects used in this analysis

```{r}
subs <- unique(data[, c("subjuuid", "sub_num")])
subs %>% arrange(sub_num)
```

```{r}
nrow(subs)
```

# Missed words

```{r}
data %>%
  select(subjuuid, word, category, sub_num, rt) %>%
  filter(rt < 0)
```

```{r}
data <- data %>%
  filter(rt >= 0)
```

# Sentiment Responses

```{r}
table(data$category, data$choice, useNA = 'always') %>% addmargins()
```

`realbad`-`f` and `realgood`-`j` cells are mismatched answers

# Mismatched responses

```{r}
data %>%
  filter((category == 'realbad' & choice == 'f') | (category == 'realgood' & choice == 'j')) %>%
  select(word, category, choice) %>%
  group_by(word, category, choice) %>%
  summarize(n = n()) %>%
  arrange(-n, word) %>%
  print(n = nrow(.))
```

# Summary Statistics on Reaction Times

```{r}
stats <- data %>%
  group_by(category) %>%
  summarize(avg_rt = mean(rt),
            sd_rt = sd(rt), 
            q1 = quantile(rt, 0.25),
            q3 = quantile(rt, 0.75))

print(stats)
```

# Slow and Fast Reaction Words

```{r}
fbt <- as.numeric(stats[stats$category == 'realbad', 'q1'])
fgt <- as.numeric(stats[stats$category == 'realgood', 'q1'])

fast_bad_words <- data[data$rt <=  fbt & data$category == 'realbad', 'word']
fast_good_words <- data[data$rt <= fgt & data$category == 'realgood', 'word']

sbt <- as.numeric(stats[stats$category == 'realbad', 'q3'])
sgt <- as.numeric(stats[stats$category == 'realgood', 'q3'])

slow_bad_words <- data[data$rt >= sbt & data$category == 'realbad', 'word']
slow_good_words <- data[data$rt >= sgt & data$category == 'realgood', 'word']
```


```{r}
fast_bad_words
fast_good_words
slow_bad_words
slow_good_words
```

# Comparison Word Cloud

```{r}
# fs_words <- c(fast_bad_words, fast_good_words, slow_bad_words, slow_good_words)

#fs_words_tbl <- tibble(fs_words) %>%
#  inner_join(data, by = c('fs_words' = 'word')) %>%

fs_words_tbl <- data %>%
  select(subjuuid, id, word, category, rt) %>%
  filter(category %in% c('realbad', 'realgood')) %>%
  mutate(rt_invert = 1 / rt) %>%
  mutate(score_flip = ifelse(category == "realgood", rt_invert, -1 * rt_invert)) %>%
  #unique() %>%
  mutate(word = reorder(word, score_flip))

words_tbl_vis <- fs_words_tbl %>%
  group_by(category, word) %>%
  summarize(speed = mean(rt_invert))

# rank the words by time
# words_tbl$rt_ranked <- 1:nrow(words_tbl)
# words_tbl$txf_rank <- words_tbl$rt_ranked

```

```{r, warning=FALSE, fig.width=8, fig.height=8}
words_tbl_vis %>%
  reshape2::acast(word ~ category, value.var = "speed", fill = 0) %>%
  comparison.cloud(colors = c("#F8766D", "#00BFC4"), scale = c(4,.5))
```

Word cloud of `readlgood` vs `realbad` categorized words.

Size of word is based on the inverse $(1 / rt)$of the `rt`, the `speed`

# Comparison Word Plot

```{r, fig.width=8, fig.height=12}
words_tbl_vis %>%
  filter(speed > .0015) %>%
  ggplot(aes(word, speed, fill = category)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    ylab("Speed") +
    coord_flip() +
    theme_minimal() +
    theme(legend.position = c(.9, 0.5))
```

Longer the bar, the faster the reponse.
The bar is the inverse of the original `rt` variable.

These results should match the word cloud

# Lengh of word

```{r}
fs_words_tbl$word_len <- nchar(as.character(fs_words_tbl$word))

base_g <- ggplot(fs_words_tbl, aes(x = as.factor(word_len), y = rt)) + theme_minimal()
```

```{r}
base_g + geom_boxplot()
```

```{r}
base_g + geom_violin()
```

```{r}
base_g + geom_boxplot(aes(color = category)) + theme(legend.position = c(0.9, 0.9))
```

```{r}
base_g + geom_violin(aes(color = category)) + theme(legend.position = c(0.9, 0.9))
```


Length of the word does not play a role in `rt`
